---
title: "Summary of analysis for survival model meta-analysis"
author: "Soumya Banerjee and Tom Bishop"
date: "1 February 2021"
output: 
  pdf_document:
    toc: true
    number_sections: yes
    fig_caption: yes
urlcolor: blue
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

# Summary

This is a document that outlines analysis using survival models
and meta-analyzing hazard ratios in the DataSHIELD platform.

# Survival analysis in DataSHIELD


All code is available here:

   * https://github.com/neelsoumya/dsBaseClient/tree/absolute_newbie_client
   
   * https://github.com/neelsoumya/dsBase/tree/absolute_newbie
   
   * https://github.com/neelsoumya/datashield_testing_basic/blob/master/development_plan.rmd
   
   * https://github.com/neelsoumya/datashield_testing_basic/blob/master/development_plan.pdf
   
   * https://github.com/neelsoumya/datashield_testing_basic/tree/master/gui/survival_models_gui
   



```{r, include = FALSE}

####################
# Load library
####################
library(knitr)
library(rmarkdown)
library(tinytex)
library(survival)
library(metafor)
library(ggplot2)
library(survminer)
require('DSI')
require('DSOpal')
require('dsBaseClient')
library(dsHelper)

```

# Model parameters

This report and the model has been run according to the following parameters.

```{r, include = FALSE}

  #`r toString()`

  # create a data frame with the parameters and model
  df_model_parameters = data.frame( cbind('Survival model', input$exposure), stringsAsFactors = FALSE )
  #df_model_parameters <- rbind(df_model_parameters, 
  #                             c(input$model, input$exposure)
  #                             )
  colnames(df_model_parameters)[1] <- "Model"
  colnames(df_model_parameters)[2] <- "Exposure"
  
```

```{r, echo = FALSE}
  
  # show the data frame
  knitr::kable(df_model_parameters)
  
```




# Meta-analysis model summary



A summary of the meta-analyzed model is shown below.


```{r, echo=FALSE}

    # cat('BEGIN LOG \n')
    #cat('Parameters: \n')
    #cat('Model : \n') 
    #cat(input$model, '\n') 
    #cat('Exposure \n')
    #cat(input$exposure, '\n\n') 
    #cat("Summary of meta-analyzed model .... \n") 
    print(meta_model)
   
```   
   
# Cox model summary

A summary of the fitted Cox model for each study is shown below.

```{r, echo = FALSE}
    
    # now print Cox model
    cat("Summary of Cox model ..... \n") 
    print(coxph_model_full) 
    
```

# Forest plot of meta-analyzed hazard ratios

We now outline the hazard ratios from the survival models which are meta-analyzed. 
We use the *metafor* package for meta-analysis. We show a forest plot below. 

```{r fig.cap="Forest plot of meta-analyzed hazard ratios.", echo=FALSE}

metafor::forest.rma(x = meta_model)

# Plotting of privacy-preserving survival curves

# We also plot privacy preserving survival curves.

# dsBaseClient::ds.survfit(formula='surv_object_prentice~1', objectname='survfit_object')
# dsBaseClient::ds.plotsurvfit(formula = 'survfit_object')

```


```    




# References

  * https://github.com/datashield
  
  * http://www.metafor-project.org
  
  * https://github.com/neelsoumya/datashield_testing_basic/tree/master/gui/survival_models_gui
  
  * https://github.com/neelsoumya/dsSurvivalShiny
  
  
  
  
  
