---
title: "Summary of data"
author: "Soumya Banerjee and Tom Bishop"
date: "1 January 2021"
output: 
  pdf_document:
    toc: true
    number_sections: yes
    fig_caption: yes
urlcolor: blue
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

# Summary

This is a document that outlines the summary of the data.


```{r, include = FALSE}

####################
# Load library
####################
library(knitr)
library(rmarkdown)
library(tinytex)
library(survival)
library(metafor)
library(ggplot2)
library(survminer)
require('DSI')
require('DSOpal')
require('dsBaseClient')
library(dsHelper)

```

# Model parameters

This report and the model has been run according to the following parameters.

```{r, include = FALSE}

  #`r toString()`

  # create a data frame with the parameters and model
  df_model_parameters = data.frame( cbind('Survival models', input$exposure), stringsAsFactors = FALSE )
  #df_model_parameters <- rbind(df_model_parameters, 
  #                             c(input$model, input$exposure)
  #                             )
  colnames(df_model_parameters)[1] <- "Model"
  colnames(df_model_parameters)[2] <- "Exposure"
  
```

```{r, echo = FALSE}
  
  # show the data frame
  knitr::kable(df_model_parameters)
  
```

# Data summary

A summary of the data, descriptive statistics and the amount of missingness is shown below.



## Descriptive statistics of data

Descriptive summary statistics of data.

```{r, include = FALSE}
    
    # now print summary of data for all covariates
    cat("Summary of covariates and missingness ..... \n") 
    # cat("Redmeat covariate  \n") 
    #print(dsBaseClient::ds.summary(x = 'D$REDMEAT'))
    cat("Summary statistics .... \n") 
    list_stats_summary <- dsHelper::dh.getStats(conns = connections, df = 'D', vars = c('REDMEAT','OFFALS','POULTRY','REDMEATTOTAL') )  
    
```

```{r, echo = FALSE}

    knitr::kable(as.data.frame(list_stats_summary$categorical))
    knitr::kable(as.data.frame(list_stats_summary$continuous))
    # print(list_stats_summary)

```

## Data quality and understanding covariates

### Missingness of covariates

The amount of missing for each covariate is shown below. The table shows if there are any covariates that are missing for any study.

```{r, include = FALSE}

    cat("Degree of missingness in various studies ..... \n") 
    dt_missingness <- dsHelper::dh.anyData(conns = connections,  df = 'D', vars = c('REDMEAT','OFFALS','POULTRY','REDMEATTOTAL') ) 
```

```{r, echo = FALSE}

    knitr::kable(dt_missingness)
    

```


### Variable types of covariates

This summarizes if the covariates are of the same type or class in each study.


```{r, include = FALSE}

  dt_type_information <- dsHelper::dh.classDiscrepancy(conns = connections, df = 'D', vars = NULL)

```

```{r, echo = FALSE}

  knitr::kable(dt_type_information)
  
```


## Quality control

We outline the number of patients who have been excluded due to the inclusion and exclusion criterion.

    
### 	Inclusion criterion

        *	 age >= 18 years

        *  Number of patients after removing those with age >= 18  

```{r, echo = FALSE}

# cat("The number of patients after removing those with age >= 18 ...")
dsBaseClient::ds.length(x = 'E_temp2$SEX', 
                        type = 'split',
                        datasources = connections)
```

###  Exclusion criterion

        * no previous diabetes

        * no type 1 diabetes
    
            * number of patients that remain after removing those with Type 1 diabetes 


```{r, echo = FALSE}
        # cat("The number of patients that remain after removing those with Type 1 diabetes  ..\n")
        dsBaseClient::ds.length(x = 'E_temp3$SEX', 
                                type = 'split',
                                datasources = connections)
```

### Exclusion due to energy intake

        * number of participants removed with very high or very low energy intake
            
```{r, echo = FALSE}
# how many have been removed
         dsBaseClient::ds.length(x = 'L2$SEX', 
                                 type = 'split',
                                 datasources = connections)

         dsBaseClient::ds.length(x = 'E3$SEX',
                                 type = 'split',
                                 datasources = connections)

```
   
```{r, include = FALSE}   
     cat("The number of patients removed due to lower bound on energy intake are: \n")
     dsBaseClient::ds.length(x = 'D_curated$SEX',
                             type = 'split',
                             datasources = connections)                        

```


# References

  * https://github.com/datashield
  
  * http://www.metafor-project.org
  
  * https://github.com/neelsoumya/datashield_testing_basic/tree/master/gui/survival_models_gui
  
  
  
  
  
